\documentclass[12pt, letterpaper, preprint, comicneue]{aastex63}
%\usepackage[default]{comicneue} % comic sans font for editing
\usepackage[T1]{fontenc}
\input{vc}
\usepackage{color}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{ctable}
\usepackage{bm}
\usepackage[normalem]{ulem} % Added by MS for \sout -> not required for final version
\usepackage{xspace}
\usepackage{csvsimple} 

\usepackage{graphicx}
\usepackage{pgfkeys, pgfsys, pgfcalendar}


% typesetting shih
\linespread{1.08} % close to 10/13 spacing
\setlength{\parindent}{1.08\baselineskip} % Bringhurst
\setlength{\parskip}{0ex}
\let\oldbibliography\thebibliography % killin' me.
\renewcommand{\thebibliography}[1]{%
  \oldbibliography{#1}%
  \setlength{\itemsep}{0pt}%
  \setlength{\parsep}{0pt}%
  \setlength{\parskip}{0pt}%
  \setlength{\bibsep}{0ex}
  \raggedright
}
\setlength{\footnotesep}{0ex} % seriously?

% citation alias

% math shih
\newcommand{\setof}[1]{\left\{{#1}\right\}}
\newcommand{\given}{\,|\,}
\newcommand{\lss}{{\small{LSS}}\xspace}

\newcommand{\Om}{\Omega_{\rm m}} 
\newcommand{\Ob}{\Omega_{\rm b}} 
\newcommand{\OL}{\Omega_\Lambda}
\newcommand{\smnu}{M_\nu}
\newcommand{\sig}{\sigma_8} 
\newcommand{\mmin}{M_{\rm min}}
\newcommand{\BOk}{\widehat{B}_0} 
\newcommand{\hmpc}{\,h/\mathrm{Mpc}}
\newcommand{\bfi}[1]{\textbf{\textit{#1}}}
\newcommand{\parti}[1]{\frac{\partial #1}{\partial \theta_i}}
\newcommand{\partj}[1]{\frac{\partial #1}{\partial \theta_j}}
\newcommand{\mpc}{{\rm Mpc}}
\newcommand{\eg}{\emph{e.g.}}
\newcommand{\ie}{\emph{i.e.}}

% cmds for this paper 
\newcommand{\gr}{g{-}r}
\newcommand{\fnuv}{FUV{-}NUV}
\newcommand{\sfr}{{\rm SFR}}
\newcommand{\ssfr}{{\rm SSFR}}
\newcommand{\mtaum}{m_{\tau,M_*}}
\newcommand{\mtaus}{m_{\tau,{\rm SSFR}}}
\newcommand{\ctau}{c_\tau}
\newcommand{\mdeltam}{m_{\delta,M_*}}
\newcommand{\mdeltas}{m_{\delta,{\rm SFR}}}
\newcommand{\cdelta}{c_\delta}
\newcommand{\eda}{EDA}


\newcommand{\specialcell}[2][c]{%
  \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}
% text shih
\newcommand{\foreign}[1]{\textsl{#1}}
\newcommand{\etal}{\foreign{et~al.}}
\newcommand{\opcit}{\foreign{Op.~cit.}}
\newcommand{\documentname}{\textsl{Article}}
\newcommand{\equationname}{equation}
\newcommand{\bitem}{\begin{itemize}}
\newcommand{\eitem}{\end{itemize}}
\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}

%% collaborating
\newcommand{\todo}[1]{\marginpar{\color{red}TODO}{\color{red}#1}}
\definecolor{orange}{rgb}{1,0.5,0}
\newcommand{\ch}[1]{{\color{orange}{\bf CH:} #1}}

\begin{document} \sloppy\sloppypar\frenchspacing 

\title{PROVABGS Probabilistic Stellar Mass Function of the BGS One-Percent
Survey} 
\date{\texttt{DRAFT~---~\githash~---~\gitdate~---~NOT READY FOR DISTRIBUTION}}

\newcounter{affilcounter}
\author{ChangHoon Hahn}
\altaffiliation{changhoon.hahn@princeton.edu}
\affil{Department of Astrophysical Sciences, Princeton University, Peyton Hall, Princeton NJ 08544, USA} 
\author{DESI collaboration} 

\begin{abstract}
    We present the probabilistic stellar mass function (pSMF) of galaxies in
    the DESI Bright Galaxy Survey (BGS), observed during the One-Percent
    Survey. 
    The One-Percent Survey was one of DESI's survey validation programs that
    was conducted from April to May 2021, before the start of the main DESI
    survey. 
    It observed with the same target selection and observing strategy as the
    main survey and successfully observed the spectra of 143,017 galaxies in
    the $r < 19.5$ magnitude-limited BGS Bright sample and 95,499 galaxies in
    the fainter surface brightness and color selected BGS Faint sample over 
    $0 < z < 0.6$.
    We derive pSMFs from posteriors of stellar mass, $M_*$, inferred from
    DESI photometry and spectroscopy using the \cite{hahn2022} PROVABGS
    Bayesian SED modeling framework. 
    We use a hierarchical population inference framework that statistically
    rigorously propagates the $M_*$ uncertainties. 
    Furthermore, we include correction weights that account for the selection
    effects and incompleteness of the BGS observations. 
    We present the redshift evolution of the pSMF in BGS as well as the pSMFs
    of star-forming and quiescent galaxies classified using average specific
    star formation rates from PROVABGS. 
    Overall, the pSMFs show good agreement with previous SMF measurements in
    the literature. 
    Our pSMFs showcase the potential and statistical power of BGS, which in its
    main survey will observe >100$\times$ more galaxies.
    Moreover, we present the population inference framework for subsequent
    population statistics measurements using BGS, which will characterize the
    global galaxy population and galaxy scaling relations at low redshifts with
    unprecendent precision. 
\end{abstract}

\keywords{
    cosmology: observations -- galaxies: evolution -- galaxies: statistics
}

% --- intro ---  
\input{intro}
% --- observations ---  
\input{obs}
% --- methods ---  
\input{provabgs}
% --- results ---  
\input{results}
% --- summary ---  
\input{summary}

\section*{Acknowledgements}
It's a pleasure to thank . 
This work was supported by the AI Accelerator program of the Schmidt Futures
Foundation.

This research is supported by the Director, Office of Science, Office of High
Energy Physics of the U.S. Department of Energy under Contract No.
DE-AC02-05CH11231, and by the National Energy Research Scientific Computing
Center, a DOE Office of Science User Facility under the same contract;
additional support for DESI is provided by the U.S. National Science
Foundation, Division of Astronomical Sciences under Contract No. AST-0950945 to
the NSF's National Optical-Infrared Astronomy Research Laboratory; the Science
and Technologies Facilities Council of the United Kingdom; the Gordon and Betty
Moore Foundation; the Heising-Simons Foundation; the French Alternative
Energies and Atomic Energy Commission (CEA); the National Council of Science
and Technology of Mexico (CONACYT); the Ministry of Science and Innovation of
Spain (MICINN), and by the DESI Member Institutions:
\url{https://www.desi.lbl.gov/collaborating-institutions}.

The DESI Legacy Imaging Surveys consist of three individual and complementary
projects: the Dark Energy Camera Legacy Survey (DECaLS), the Beijing-Arizona
Sky Survey (BASS), and the Mayall z-band Legacy Survey (MzLS). DECaLS, BASS and
MzLS together include data obtained, respectively, at the Blanco telescope,
Cerro Tololo Inter-American Observatory, NSF’s NOIRLab; the Bok telescope,
Steward Observatory, University of Arizona; and the Mayall telescope, Kitt Peak
National Observatory, NOIRLab. NOIRLab is operated by the Association of
Universities for Research in Astronomy (AURA) under a cooperative agreement
with the National Science Foundation. Pipeline processing and analyses of the
data were supported by NOIRLab and the Lawrence Berkeley National Laboratory.
Legacy Surveys also uses data products from the Near-Earth Object Wide-field
Infrared Survey Explorer (NEOWISE), a project of the Jet Propulsion
Laboratory/California Institute of Technology, funded by the National
Aeronautics and Space Administration. Legacy Surveys was supported by: the
Director, Office of Science, Office of High Energy Physics of the U.S.
Department of Energy; the National Energy Research Scientific Computing Center,
a DOE Office of Science User Facility; the U.S. National Science Foundation,
Division of Astronomical Sciences; the National Astronomical Observatories of
China, the Chinese Academy of Sciences and the Chinese National Natural Science
Foundation. LBNL is managed by the Regents of the University of California
under contract to the U.S. Department of Energy. 
The complete acknowledgments can be found at
\url{https://www.legacysurvey.org/}.

The authors are honored to be permitted to conduct scientific research on
Iolkam Du’ag (Kitt Peak), a mountain with particular significance to the Tohono
O’odham Nation.

\appendix
\input{spec_comp}
\input{jack}
\input{mscomp}

\bibliographystyle{mnras}
\bibliography{psmf} 
\end{document}
